Textmining in Economics

### 2017-10-27 paper/R/02_prepare.Rmd
facebook paper

```{r}
pat <- 'Hinweis.+?(?=(einfügen))'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

  # FOCUS.de
  x = gsub("FOCUS Online/Wochit", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub('Im Interesse unserer User[^"]*', "", x, perl = TRUE)
  x = gsub('Sie haben noch 800[^"]*', "", x, perl = TRUE)
  x = gsub('Erzählen Sie auf FOCUS Online über Ihren Heimatort Teilen Sie Ihren Artikel und Ihr Foto', "", x, perl = TRUE)
  x = gsub("Bericht schreiben", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub("Hier können Sie selbst Artikel verfassen:","", x)
  x = gsub("Live-Ticker", "", x)

@@

@@

## Save by Site
```{r}
save_by_site <- function(DF) {
  write.csv(DF, paste0("../output/single/",as.character(DF),".csv"))
  return(DF)
}

df %>%
  group_by(site) %>%
  do(save_by_site(.))
```

```{r}
df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/single/stern.csv")
df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/single/focus.csv")
df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/single/zeit.csv")
df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/single/wdr.csv")
df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/single/spiegel.csv")
df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/single/welt.csv")
df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/single/handelsblatt.csv")
df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/single/tagesschau.csv")
df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/single/swr.csv")
df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/single/bild.csv")
df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/single/ndr.csv")
```

## Load by site
```{r}
focus <- read.csv("../output/focus.csv")
spiegel <- read.csv("../output/spiegel.csv")
bild <- read.csv("../output/bild.csv")

df_reduced <- rbind(focus, spiegel, bild)
```

```{r}
save(df_reduced, file="../output/df_reduced.Rda")
```

>>>>

```{r}
pat <- 'Aus unserem Netzwerk[^"]*'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

  # FOCUS.de
  x = gsub("FOCUS Online/Wochit", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub('Im Interesse unserer User[^"]*', "", x, perl = TRUE)
  x = gsub('Sie haben noch 800[^"]*', "", x, perl = TRUE)
  x = gsub('Erzählen Sie auf FOCUS Online über Ihren Heimatort Teilen Sie Ihren Artikel und Ihr Foto', "", x, perl = TRUE)
  x = gsub("Bericht schreiben", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub("Hier können Sie selbst Artikel verfassen:","", x)
  x = gsub("Live-Ticker", "", x)
  x = gsub('Aus unserem Netzwerk[^"]*', "", x, perl = TRUE)

@@

```{r}
# Save file
save(df, file="../output/news_cleaned2.Rda")
```

@@

## Generate new variables 
```{r}
df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
df$date <- as.Date(df$date)
```

## Reduce Dataframe
```{r}
df %>%
  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw

btw$ArticleID <- rownames(btw)
```

```{r}
save(df, btw, file="../output/news_btw.Rda")
```

### 2017-10-27 paper/R/05_lda_eight2late.Rmd
facebook paper

```

@@

save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

@@

### Create Topic Labels
As part of the visualization I will construct later, a topic label needs be used to created. The terms are gathered in rank order and then the label is created by concatenating the first three terms.

```{r}
topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

>>>>

btw$ArticleID <- rownames(btw)
```

@@

save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

@@

### Create Topic Labels
```{r}
topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

### 2017-10-27 paper/R/06_explore_LDA.Rmd
facebook paper

## Load Data
```{r}
rm(list = ls())

load("../output/news_cleaned2.Rda")

df$date <- as.Date(df$date)

#col <- brewer.pal(12, name = "Paired")
```

## Reduce Dataframe
```{r}
df %>%
  filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

btw$ArticleID <- rownames(btw)
```

# Topic Modeling
## Build Corpus
```{r}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw
```

```{r}
# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)
# Assign name to docs
rownames(dtm) <- make.unique(btw$title)

inspect(dtm)
```

## Run LDA using Gibbs sampling
```{r}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

k = 50 # Topics
```

```{r}
t1 <- Sys.time()
lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

```{r}
#write out results (docs to topics)
ldaOut.topics <- as.matrix(topics(ldaOut))
write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
```

```{r}
#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,6))
write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
#rownames(topicProbabilities) <- make.unique(btw$title)

write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
```

```{r}
#Find relative importance of top 2 topics
topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
```

```{r}
#Find relative importance of second and third most important topics
topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
```

```{r}
#write to file
write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
```

## Explore the model
```{r}
load(file ="../output/models/LDAGibbs 50 .Rda")
```

@@

doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)
doctopics.df[1:10,]

# Add Topic to origian DF
```

### Most likely Words per Topic
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
btw.terms[1:5,1:10]
```

@@

```{r}
x <- as.data.frame(row.names(theta), stringsAsFactors = FALSE)
#colnames(x) <- c("ArticleID")
#x$ArticleID <- as.numeric(x$ArticleID)

#theta2 <- cbind(x,theta)
```

@@

c <- cor(theta)
corrplot(c, method = "circle")
```

>>>>

## Load Data
```{r}
rm(list=ls())

load(file ="../output/models/LDAGibbs 50 .Rda")
```

@@

doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)

# Add Topic to origian DF
btw <- btw %>%
  mutate(ArticleID = as.integer(ArticleID)) %>%
  inner_join(.,doctopics.df, by="ArticleID")
```

### Most likely Words per Topic
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
btw.terms[1:10,10:12]
```

@@

Correlate the topic by news source of the documents. The column means of theta, grouped by news source is calculated.

```{r}
x <- as.data.frame(row.names(theta), stringsAsFactors = FALSE)
colnames(x) <- c("ArticleID")
x$ArticleID <- as.numeric(x$ArticleID)

theta2 <- cbind(x,theta)
theta2 <- dplyr::left_join(theta2, btw[,c("site", "ArticleID")], by="ArticleID")

## Column means grouped by news outlet
theta.mean.by <- by(theta2[,2:51], theta2$site, colMeans)
theta.mean <- do.call("rbind", theta.mean.by)
```

@@

c <- cor(theta.mean)
corrplot(c, method = "circle")
```

Using the categories mean theta, it is possible to select the most diagnostic topic for each of the categories.

```{r}
theta.mean.ratios <- theta.mean
for (ii in 1:nrow(theta.mean)) {
  for (jj in 1:ncol(theta.mean)) {
    theta.mean.ratios[ii,jj] <-
      theta.mean[ii,jj] / sum(theta.mean[ii,-jj])
  }
}

topics.by.ratio <- apply(theta.mean.ratios, 1, function(x) sort(x, decreasing = TRUE, index.return = TRUE)$ix)

# the most diagnostic topics per news source are found in the thea 1st row of index matrix
topics.by.ratio[1:10,]
```

### compute cosine similarity

```{r, message=FALSE}
library(proxy)
cosine_dist <- as.matrix(dist(topics.by.ratio, by_rows = FALSE, method = "cosine"))
```

### Correlogram
```{r, message=FALSE}
devtools::install_github("sinhrks/ggfortify")
library("ggfortify")
devtools::install_github("kassambara/ggcorrplot")
library(ggcorrplot)
library("ggthemes")

ggcorrplot(cosine_dist, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           #colors = c("tomato2", "white", "springgreen3"), 
           title="", 
           ggtheme=theme_bw)
```

## Regression
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#library(GGally)

btw_reduced <- btw[,c(1,6,10,13,14,15)]

ggpairs(btw_reduced, aes(color = site, alpha=.5))
```

```{r}
library(plm)

lm1 <- lm(fb_shares ~ Topic1 * site, data = btw)
summary(lm1)
```

### 2017-10-27 paper/R/06_stm.Rmd
facebook paper

@@

```{r, eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(df$text_cleaned, metadata = df[,c("date","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Run the Model 
```{r}

t1 <- Sys.time()
stm <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=25, 
           prevalence = ~site, 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(stm, out, file = "stm.RDa")
#load(file = "stm.RDa")

@@

### compute cosine similarity

```{r, message=FALSE}
library(proxy)
cosine_dist <- as.matrix(dist(as.matrix(source_mean[,1:20]), method = "cosine"))
colnames(cosine_dist) <- unique(out$meta$source)
rownames(cosine_dist) <- unique(out$meta$source)
```

### Correlogram
```{r, message=FALSE}
devtools::install_github("sinhrks/ggfortify")
library("ggfortify")
devtools::install_github("kassambara/ggcorrplot")
library(ggcorrplot)
library("ggthemes")

ggcorrplot(cosine_dist, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           #colors = c("tomato2", "white", "springgreen3"), 
           title="", 
           ggtheme=theme_bw)
```

@@

```.

>>>>

btw$ArticleID <- rownames(btw)
```

@@

```{r, eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Run the Model 
```{r}
k = 50 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=k, 
           prevalence = ~site, 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(stmOut, btw, file=paste("../output/models/STM",k,".Rda"))

@@

@@

### 2017-10-27 paper/doc/doc2.tex
facebook paper

The debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media. But it is precisely this competitiveness that is constitutionally guaranteed. On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The regulator recognizes this inequality and has banned advertising and sponsorship in its online services.

The fundamental question in this debate is whether the offer of public news on the internet is justified. They should only occur where there are clear deficits in private sector supply. A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest. Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest. Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.

Markt für Online-Texte.
Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote. "Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)

Wettbewerb im "Gemischten Oligopol": Die kostenlosen Nachrichtenangebote von ZDF.de oder tagesschau.de im Internet konkurrieren hier mit den Online Angeboten der klassischen Printmedien. Die beitragsfinanzierten Angebote behindern in der Tendenz Prozesse, durch die sich ein selbst tragendes, qualitativ hochwertiges Subskriptionssystem privatwirtschaftlicher Anbieter (spiegel.de, faz.net, welt.de, ...) entwickeln kann.

\begin{itemize}
	\item Reserach Question
	\begin{itemize}
		\item Analyzing news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
		\item Quantify the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
	\end{itemize}
	\item Method
	\begin{itemize}
		\item Topical content of documents, in which mixing weights are parameterized by observed covariates
		\item Topic distribution word-topic distribution are specified as a simple generalized linear model on an arbitrary number of document-level covariates (news source, time of release).
	\end{itemize}
\end{itemize}

Text as a data source is becoming increasingly popular in empirical economics, as the information encoded in text is a rich complement to conventional data (e.g. price, wage, votes, etc.) (\citet{grimmer_bayesian_2010}; \citet{grimmer_text_2013}; \citet{quinn_how_2010}; \citet{gentzkow_text_2017}; \citet{roberts_model_2016}). On interesting question is, how document metadata such as author or date influence its content. Depending on the characteristics of a corpus (a collection of documents), documents contain more than one topic, as well as terms most likely appear in multiple topics, thus the use of mixed-membership models \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} - are a popular approach.

Within these models the Latent Dirichlet Allocation (LDA hencefirth) is a widely used topic modelling technique, where each document is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution). To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used. LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}. Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.

\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.

@@

% Politics and Newspaper
% ----------------------

In \citet{tetlock_giving_2007}, $c_i$ is a bag-of-words representation and the outcome of interest $v_i$ is the latent “sentiment” of Wall Street Journal columns, defined along a number of dimensions such as “positive,” “optimistic,” and so on. The author defines the function $f (\cdot)$ using a dictionary called the General Inquirer, which provides lists of words associated with each of these sentiment categories.2 The elements of $f(c_i)$ are defined to be the sum of the counts of words in each category.

@@

>>>>

Social networks such as Facebook are becoming increasingly important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media into an important generator of traffic on the internet pages. In Germany, 94\% of online news articles are shared on Facebook in 2015, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are often shared on Facebook. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.

While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared). Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. To take these factors into account, we use a mixed-membership model \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares.

Within topic models the Latent Dirichlet Allocation (LDA henceforth) is a widely used topic modeling technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution). To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used. LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}. Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.

\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services. We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.

@@

@@

% -----
% Data
% -----

\section{Data}

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from f

% ---------------------------------
% Generative Process
% ----------------------------------
